Analysis of the inference of ratings and rankings on Higher Order Networks with complex topologies

### 2025-07-13 draft/draft.tex
progress

The data comprehends 5 soccer leagues from England, France, Germany, Italy and Spain.
Each has 20 teams, with the exception of Germany which has 18.
Each pair of teams of each league plays two games, one as local and another the visitor.
For each game between two teams $i$ and $j$ of a given league, a score $\phi_{ij}\in \RR$ is provided.

>>>>

The data comprehends 5 soccer leagues from England, France, Germany, Italy and Spain.
Each has 20 teams, with the exception of Germany which has 18.
For each pair of teams $i$ and $j$ of a given league, a score $\phi_{ij}\in \RR$ is provided, which is the aggregate of the two games between them, one as a local and another as a visitor.
There are ten different types of scores:
\begin{enumerate}
\item {\bf crossings:}
\item {\bf counterattacks:}
\item {\bf pressure loss:}
\item {\bf build-up time:}
\item {\bf direct play:}
\item {\bf pressure points:}
\item {\bf shots:}
\item {\bf flow rate:}
\item {\bf maintenance time:}
\item {\bf middle-zone time:}
\end{enumerate}
